Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-06-13 tex/paper1/paper1.tex
changes to the paper and the plots

Model selection is implemented using the Akaike Information Criterion
(AIC) and the Bayesian Information Criterion (BIC)
\citep{2007MNRAS.377L..74L}.  The AIC is defined as
\begin{equation}\label{eqn:aic}
AIC \equiv -2 \ln L_{max} - 2k
\end{equation}
where $L_{max}$ is the maximum likelihood achievable by the model, and
$k$ is the number of parameters in the model.  The BIC is defined as
\begin{equation}\label{eqn:bic}
BIC \equiv -2 \ln L_{max} - k\ln N
\end{equation}
where $N$ is the number of data points used in the fit.  Model
selection is guided by calculating $\delta AIC = AIC_{1} - AIC_{2}$
and $\delta BIC = BIC_{1} - BIC_{2}$.  Positive values of $\delta AIC,
\delta BIC$ express a preference for model 2 over model 1.

For both the AIC and the BIC, Model 2 is overwhelmingly preferred to
Model 1. Table \ref{tab:parameters} gives the parameter estimates and
68\% credible intervals of the parameter values.  The power law
indices for all regions and both wavebands lie in the range 1.8 to
2.3, although there is no consistency between one waveband and
another.  For example, the 171\AA\ and 193\AA\ loop footpoint results
both have the same power law index, but the other regions do not.
However, it should be noted that there is no {\it a priori} reason why
the power law indices for a region seen in two different wavebands
should be the same.  This is because each waveband is designed to
examine different features on the Sun in broadly different temperature
ranges, and may be imaging very different physical processes: hence,
the emission seen in one waveband need not have the same statistical
properties as another

@@

Models are selected using the Akaike and Bayesian Information Criteria
\cite{???} calculated using the final parameter estimates of Models 1
and 2.

>>>>

Model selection is implemented using the Akaike Information Criterion
(AIC) and the Bayesian Information Criterion (BIC)
\citep{2007MNRAS.377L..74L}.  The AIC is defined as
\begin{equation}\label{eqn:aic}
AIC \equiv -2 \ln L_{max} - 2k
\end{equation}
where $L_{max}$ is the maximum likelihood achievable by the model, and
$k$ is the number of parameters in the model ($k=3$ for Model 1, and
$k=6$ for Model 2).  The BIC is defined as
\begin{equation}\label{eqn:bic}
BIC \equiv -2 \ln L_{max} - k\ln N
\end{equation}
where $N$ is the number of data points used in the fit (in this case
$N=899$, the number of non-zero frequencies of the Fourier power
spectrum).  Model selection is guided by calculating $\delta AIC =
AIC_{1} - AIC_{2}$ and $\delta BIC = BIC_{1} - BIC_{2}$.  Positive
values of $\delta AIC, \delta BIC$ express a preference for model 2
over model 1.

Using both the AIC and the BIC, Model 2 is overwhelmingly preferred to
Model 1 (see Figure \ref{fig:fit171193}). Table \ref{tab:parameters}
gives the parameter estimates and 68\% credible intervals of the
parameter values.  The power law indices for all regions and both
wavebands lie in the range 1.8 to 2.3, although there is no
consistency between one waveband and another.  For example, the
171\AA\ and 193\AA\ loop footpoint results both have the same power
law index, but the other regions do not.  However, it should be noted
that there is no {\it a priori} reason why the power law indices for a
region seen in two different wavebands should be the same.  This is
because each waveband is designed to examine different features on the
Sun in broadly different temperature ranges, and may be imaging very
different physical processes: hence, the emission seen in one waveband
need not have the same statistical properties as any other.

@@

Models are selected using the Akaike and Bayesian Information Criteria
\cite{2007MNRAS.377L..74L} calculated using the final parameter
estimates of Models 1 and 2.
